---
title: "My Quarto Report"
author: Dr. Bjorn
format: html
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(here)
interviews <- read_csv(here("data/SAFI_clean.csv"), na = "NULL")
interviews_plotting <- read_csv(here("data_output/interviews_plotting.csv"))

percent_wall_type <- interviews_plotting %>% 
  filter(respondent_wall_type != "cement") %>% 
  count(village, respondent_wall_type) %>% 
  group_by(village) %>% 
  mutate(percent = (n / sum(n)) * 100) %>% 
  ungroup()
```

# Title
## Heading
### Subheading
#### Subsubheading

## Introduction

This is an *introduction*. A ***VERY*** **brief** introduction. This text is
just filler because I need to show how line breaks work.

Oh yea, we should talk about SAFI.   
The dataset.

## Materials and methods

The SAFI dataset has the following variables:

- village
  + name of village
- interview_date
  * date of the interview
    + self-explanatory
- no_members
- years_liv

Here are my favourite variables:

1. no_members
2. village
3. years_liv

## Results

```{r}
#| label: tbl-my-first-table
#| echo: false
#| message: false
#| tbl-cap: "This is where my informative caption lives."
interviews %>%
  filter(!is.na(memb_assoc)) %>% # remove NAs
  group_by(village, memb_assoc) %>% 
  summarise(mean_no_membrs = mean(no_membrs)) %>% 
  knitr::kable()
```

Here is a plot.

```{r}
#| label: fig-my-first-plot
#| echo: false
percent_wall_type %>% 
  ggplot(aes(
    x = village, 
    y = percent, 
    fill = respondent_wall_type)
  ) +
  geom_col()
```

I can refer to my table (@tbl-my-first-table) and figure (@fig-my-first-figure) in the text.




